### 2024-10-16 README.Rmd
moved vignette to meet CRAN policy

**cols4all** is an R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series. Own palettes series can be added as well.

@@

This gave us inspiration to develop own palettes: see these `cols4all` palettes below.

@@

Say we need a diverging palette that is color blind friendly, and what to choose one by eye. Then filter by "Colorblind-friendly" and sort by "Huddle Middle L" (the hue of the left wing):

@@

We applied a basic heuristics to explore palettes that score well on a mix of the properties named above

@@

## Other R funtions

@@

There are a few other pacakges with a large collection of color palettes, in particular [**pals**](https://kwstat.github.io/pals/) and [**paletteer**](https://github.com/EmilHvitfeldt/paletteer). There are a few features that distinguishes **cols4all** from those packages:

>>>>

**cols4all** is an R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series. Users can also add their own palette series.

@@

This inspired us to develop our own palettes: see these `cols4all` palettes below.

@@

Say we need a diverging palette that is color blind friendly, and what to choose one by eye. Then filter by "Colorblind-friendly" and sort by "Hue Middle L" (the hue of the left wing):

@@

We applied a basic heuristic to explore palettes that score well on a mix of the properties named above

@@

## Other R functions

@@

There are a few other packages with a large collection of color palettes, in particular [**pals**](https://kwstat.github.io/pals/) and [**paletteer**](https://github.com/EmilHvitfeldt/paletteer). There are a few features that distinguish **cols4all** from those packages:
